A Longitudinal Analysis of the Privacy Paradox

### 2020-05-07 analyses.Rmd
- Implemented feedback from reviews - Toned down implications - First language edits

```{r Corrplot, fig.height = 8, fig.width = 8, size=5}
colnames(d_fs) <- c("Concerns\nT1", "Concerns\nT2" , "Concerns\nT3",
                    "Pos. Attitude\nT1", "Pos. Attitude\nT2" , "Pos. Attitude\nT3",
                    "Inf. Sharing\nT1", "Inf. Sharing\nT2" , "Inf. Sharing\nT3")

>>>>

```{r Corrplot, fig.height = 8, fig.width = 8, size=5}
colnames(d_fs) <- c("Privacy\nconcerns\nT1", "Privacy\nconcerns\nT2" , "Privacy\nconcerns\nT3",
                    "Positive\nattitude\nT1", "Positive\nattitude\nT2" , "Positive\nattitude\nT3",
                    "Information\nsharing\nT1", "Information\nsharing\nT2" , "Information\nsharing\nT3")

### 2020-05-07 analyses_additional.Rmd
- Implemented feedback from reviews - Toned down implications - First language edits

With Factor Scores, control variables, and 4 waves / 1 year intervals

@@

>>>>

Same model, but with unconstrained effects. That way, we can empirically test the assumption whether effects have changed over time.
With Factor Scores, control variables, and 4 waves / 1 year intervals

```{r}
model_free <- '
# between relations
pri_con_b =~ 1*t1_pri_con_fs + 1*t2_pri_con_fs + 1*t3_pri_con_fs
inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t2_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs
inf_sha_att_b =~ 1*t1_inf_sha_att_fs + 1*t2_inf_sha_att_fs + 1*t3_inf_sha_att_fs

# within person effects
t2_pri_con_w ~ a1*t1_pri_con_w + t1_inf_sha_att_w + t1_inf_sha_beh_w
t2_inf_sha_att_w ~ t1_pri_con_w + b2*t1_inf_sha_att_w + t1_inf_sha_beh_w
t2_inf_sha_beh_w ~ t1_pri_con_w + t1_inf_sha_att_w + c3*t1_inf_sha_beh_w
t3_pri_con_w ~ a1*t2_pri_con_w + t2_inf_sha_att_w + t2_inf_sha_beh_w
t3_inf_sha_att_w ~ t2_pri_con_w + b2*t2_inf_sha_att_w + t2_inf_sha_beh_w
t3_inf_sha_beh_w ~ t2_pri_con_w + t2_inf_sha_att_w + c3*t2_inf_sha_beh_w

# covariances
pri_con_b ~~ cor_b_1*inf_sha_att_b + cor_b_2*inf_sha_beh_b
inf_sha_att_b ~~ cor_b_3*inf_sha_beh_b
t1_pri_con_w ~~ cor_w_1*t1_inf_sha_att_w + cor_w_2*t1_inf_sha_beh_w
t1_inf_sha_att_w ~~ cor_w_3*t1_inf_sha_beh_w
t2_pri_con_w ~~ t2_inf_sha_att_w + t2_inf_sha_beh_w
t2_inf_sha_att_w ~~ t2_inf_sha_beh_w
t3_pri_con_w ~~ t3_inf_sha_att_w + t3_inf_sha_beh_w
t3_inf_sha_att_w ~~ t3_inf_sha_beh_w

# control variables
t1_pri_con_fs ~ age + edu_num + male
t2_pri_con_fs ~ age + edu_num + male
t3_pri_con_fs ~ age + edu_num + male
t1_inf_sha_beh_fs ~ age + edu_num + male
t2_inf_sha_beh_fs ~ age + edu_num + male
t3_inf_sha_beh_fs ~ age + edu_num + male
t1_inf_sha_att_fs ~ age + edu_num + male
t2_inf_sha_att_fs ~ age + edu_num + male
t3_inf_sha_att_fs ~ age + edu_num + male
'
fit_free <- sem(model_free, data = d_wide, orthogonal = TRUE, missing = "ML")
summary(fit_free, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
effect_std_ci_free <- standardizedsolution(fit) %>% 
  filter(lhs == "pri_con_b", rhs == "inf_sha_beh_b")

# model comparison
(model_comp <- anova(fit_riclpm, fit_free))
```
Shows that model with freely estimated parameters does not show significantly improved fit.

@@

```{r include=F}
save.image("data/workspace.RData")
```
